Survivable Set Connectivity

### 2015-05-13 draft.tex
referencing image

\begin{figure}
\centering
\label{fig:rackecut}
\includegraphics[width=0.5\linewidth]{Rackecut.pdf}
\caption{R\"{a}cke's tree cut induced by an edge in the tree.}
\end{figure}

@@

@@

Figure~\ref{fig:racketree} gives an example of the flow correspondence between a graph and it's associated R\"{a}cke's tree. Each red vertex of the tree is mapped to another red vertex on the graph, and the edge between them corresponds to a path between the red vertices. This gives us a simple way to map flows from R\"{a}cke's trees to the graph and vice-versa.

\begin{figure}
\label{fig:racketree}
\centering
\includegraphics[width=0.8\linewidth]{Rackeembeddinggraph.pdf}
\caption{Example Racke Tree where red nodes are mapped and edge maps to a path.}
\end{figure}

There are some crucial properties of R\"{a}cke's trees which we will treat as black boxes. We will define these as lemmas without proof, and we refer to [CITE] for the proofs.

@@

The important property of the algorithm can be summarized in the following lemma, whose proof can be found in [CITE].

@@

If we know $\sum_{i=1}^h |S_i| = S$ is small (the number of sources is small). We can run the algorithm without looking for the nodes where the flow paths turn. In particular, we could treat it as many different instances of the Group Steiner Tree problem. The algorithm would be:
\begin{codebox}
\li Set $H \leftarrow \emptyset$
\li Compute linear program SSC-LP and set to zero any $x_e < \dfrac{k}{n^2}$.
\li Let $x' \leftarrow x*\frac{4}{k}$. 
\li Prepare $\mathcal{D}$, the distribution of R'\"{a}cke's tree embeddings for $G$ with $x'$.
\li \For $\tau$ rounds \Do
\li Sample $(T, y, \text{map})$ from $\mathcal{D}$. 
\li \For $q = 0, ..., 2\log n$ \Do
\li \For \For $i \in [h]$ and $s \in S_i'$ \Do
\li With probability $\min\{1, \dfrac{4}{2^q}\}$, $q$-mark $s$
\li \If $s$ is $q$-marked \Then
\li Set $y^{s, q}\leftarrow 2^{q+1}y$ and $E^{s,q} \leftarrow \emptyset$.
\li \For $\tau'$ iterations, \Do
\li $E^{s,q} \leftarrow E^{s,q} \cup$ RoundGKR$(T_s, s, y^{s,q})$ \End
\li $H \leftarrow H \cup \text{map}(E^{s,q})$ \End \End \End \End
\li return $H$
\end{codebox}
The main difference lies in line 8. Instead of iterating through all $v \in V_T$ to find where the flow path turns, we take advantage of knowing where the flow begins. We know all flow paths go from $S_i'$ to $T_i'$, so we make $s \in S_i'$ the root of the tree. It is unnecessary to look for where the flow turns. We still have to iterate through $q= 0, ..., 2\log n$, since the flow of at least $1$ between $S_i'$ and $T_i'$ might be divided among different flow paths starting at different nodes in $S_i'$. This gets rid of the $O(\log n)$ factor in the cost because of the height, and adds a factor of $S$.

>>>>

@@

Figure~\ref{fig:racketree} shows an example R\"{a}cke's tree. We see a tree on the left-hand side which corresponds to the graph on the right-hand side. Each node is labeled by a number. The number indicates the projection of $\mathrm{map}$. A node of the tree labeled $1$ corresponds to the node in the graph labeled $1$. As you can see, the leaves are in bijection with the nodes of the graph.

In addition, edges in the tree correspond to paths in the graph. The bolded edges of the tree map to the bolded edges in the graph. The top-most edge in the tree connects nodes $3$ and $5$, and that edge maps to the edge in the graph connecting $3$ and $5$. Then the bolded edge in the tree connecting $5$ to $5$ corresponds to the empty path. The bolded edge of the tree connecting $5$ to $4$ corresponds to the bolded edge in the graph connecting $4$ and $5$. Paths in the tree correspond to paths in the graph.

We also note the capacity of the edge in the tree labeled $y$ is $x_1 + x_2 + x_3$. Edge $y$ disconnects the leaves into two groups, $S'$ and the rest. $S'$ maps bijectively to $S$. $S$ induces a cut on the graph, which cuts edges $x_1$, $x_2$, and $x_3$. Therefore, the capacity of $y$ (as defined by R\"{a}cke's trees) is the sum of the capacities of $x_1,x_2,$ and $x_3$.

Another thing to notice is that $load(x_1) = 0$, since $\mathrm{map}^{-1}(x_1) = \emptyset$. An immediate consequence, which we can see from the load is that removing an edge with load 0 does not affect the connectivity of the graph. At a high level, the load will measure how necessary an edge is for connectivity.

\begin{figure}
\label{fig:racketree}
\includegraphics[width=\linewidth]{RackeTree.pdf}
\caption{A R\"{a}cke's tree example. A R\"{a}cke tree on the left maps to a graph on the right. The map on vertices is defined by the labelings on the nodes. The bolded edges map to the bolded edges. Edge $y$ defines a set of leaves $S'$, which defines a cut on the graph, $S$. $S$ cuts edges $x_1, x_2,$ and $x_3$; therefore, $y = x_1 + x_2 + x_3$.}
\end{figure}

@@

There are some crucial properties of R\"{a}cke's trees which we will treat as black boxes. We will define these as lemmas without proof, and we refer to \cite{racke} for the proofs.

@@

The important property of the algorithm can be summarized in the following lemma, whose proof can be found in \cite{GKR}.

@@

If we know $\sum_{i=1}^h |S_i| = S$ is small (the number of sources is small). We can run the algorithm without looking for the nodes where the flow paths turn. In particular, we could treat it as many different instances of the Group Steiner Tree problem. The algorithm would be:
\begin{codebox}
\li Set $H \leftarrow \emptyset$
\li Compute linear program SSC-LP and set to zero any $x_e < \dfrac{k}{n^2}$.
\li Let $x' \leftarrow x*\frac{4}{k}$. 
\li Let $\mathcal{D}$ be the distribution of R\"{a}cke's tree embeddings for $G$ with $x'$.
\li \For $\tau$ rounds \Do
\li Sample $(T, y, \text{map})$ from $\mathcal{D}$. 
\li \For $q = 0, ..., 2\log n$ \Do
\li \For \For $i \in [h]$ and $s \in S_i'$ \Do
\li With probability $\min\{1, \dfrac{4}{2^q}\}$, $q$-mark $s$
\li \If $s$ is $q$-marked \Then
\li Set $y^{s, q}\leftarrow 2^{q+1}y$ and $E^{s,q} \leftarrow \emptyset$.
\li \For $\tau'$ iterations, \Do
\li $E^{s,q} \leftarrow E^{s,q} \cup$ RoundGKR$(T_s, s, y^{s,q})$ \End
\li $H \leftarrow H \cup \text{map}(E^{s,q})$ \End \End \End \End
\li return $H$
\end{codebox}
The main difference lies in line 8. Instead of iterating through all $v \in V_T$ to find where the flow path turns, we take advantage of knowing where the flow begins. We know all flow paths go from $S_i'$ to $T_i'$, so we make $s \in S_i'$ the root of the tree. It is unnecessary to look for where the flow turns. We still have to iterate through $q= 0, ..., 2\log n$, since the flow of at least $1$ between $S_i'$ and $T_i'$ might be divided among different flow paths starting at different nodes in $S_i'$. This gets rid of the $O(\log n)$ factor in the cost because of the height, and adds a factor of $S$.
